Using Statistical Methods to Predict the Outcome of Basketball Games

### 2021-03-29 proposal/proposal.Rmd
adding proposal

```{r, include=FALSE}
source(here::here("R", "explatoryAnalysis.R"))
```

# 1. Data

Our data comes from three different data sources Kaggle, NCAA, and a March Madness bracket. First, a Kaggle^[https://www.kaggle.com/c/ncaam-march-mania-2021/data] machine learning challenge that has a comprehensive records of every US division I basketball game played from 2003 to 2020. Second, the NCAA^[http://stats.ncaa.org/rankings/change_sport_year_div] team statistics. Third, the tournament bracket in a nice .xls format we obtained from a blog^[https://plexkits.com/march-madness-bracket/].

@@

Our response is the outcome win/loss as a function of team statistics. 
win 
`r #TODO: fill this out maybe make this a list if its too big`

|  Variable name     |  Description  |   Type  |
| ------------------ | ------------- | ------- |
| win                |               |         |
| fg_percent         |               |         |
| opposingfg_percent |               |         |
| ft_percent         |               |         |
| opposingft_percent |               |         |
| rpg                |               |         |
| opposingrpg        |               |         |
| st                 |               |         |
| opposingst         |               |         |
| to                 |               |         |
| opposingto         |               |         |
| opposingbkpg       |               |         |
| bkpg               |               |         |

>>>>

```{r, include=FALSE}
# source(here::here("R", "explatoryAnalysis.R"))
```

# 1. Data
 ^[https://plexkits.com/march-madness-bracket/].

@@

Our response is the outcome win/loss as a function of team statistics. Win or loss coded 0 or 1. field goal precentage, 
win,fg_percent, opposingfg_percent, ft_percent, opposingft_percent, rpg, opposingrpg, st, opposingst, to, opposingto, opposingbkpg, bkpg
